---
title: "Lab5InYourFace"
author: "Eric Herwin and Albin Västerlund"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

knitr::opts_chunk$set(fig.width=7, fig.height=7) 

```

This package contains two function who help's you to get the Longitude and Latitude of a address/destination so you can plot a map of the address/destination. 

## The function

1. **data_address:** 
    + Input:
*address*
    + Returns:
Returns a data.frame of longitude and latitude for the address/destination 

2. **plot_address:** 
    + Input:
*address* and *zoom*
    + Returns:
Returns a plot of the address/destination



## Examples
Here is example of how to use the functions data_address and plot_address!

### data_address

```{r,echo=FALSE,message=FALSE}
library(Lab5InYourFace)

```


```{r,message=FALSE}
data_address("Stockholm")

data_address("sweden")

```

### plot_address
```{r,message=FALSE}
plot_address("Stockholm",zoom=12)


```



```{r,message=FALSE}
plot_address("sweden",zoom=4)


```
