---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:


```{r,echo=FALSE, message=FALSE}
library(mlbench)
library(caret)
library(Lab7SpaghettiBolognese)
data("BostonHousing")
```


## 1)

We will devide the `BostonHousing` dataset in to a training and a test set.

```{r}
training <- createDataPartition(BostonHousing$tax,p = 0.7)

train_data <- BostonHousing[training$Resample1, ]
test_data <- BostonHousing[-training$Resample1, ]
```




## 2)

This is our linear model with the variable `tax`.

```{r}
model_lm <- train(tax ~ .  ,data = train_data, method = "lm")
sol <- summary(model_lm)
sol$coefficients
```

This for evaluating this model we perform a forward selection of the model.

```{r}
model_leap_forward <- train(tax ~ .  ,data = train_data, method = "leapForward")

hej <-summary(model_leap_forward)
hej$which


```

We can see that the model choosen contains the expnatory variables: `zn`, `indus`, `rad` and `medv`. 



## 3)

```{r}
model_lm <- train(tax ~ zn + indus + rad + medv  ,data = train_data, method = "lm")
summary(model_lm)
```

We rate this model!


## 4)


```{r}
ridgereg$new(tax ~ zn + indus + rad + medv, data=train_data ,lambda=seq(0.1,0.5,0.1))$print()
```










